Temporary Trade Barriers: \\ When Will They End?

### 2016-05-13 presentation.tex
add two more results

\begin{frame}{Government}
  $G$ renews AD duties if its utility is higher under AD duties than trade agreement tariff
  \begin{itemize}
		\item Preferences are ex-ante uncertain through $\ta$
		\pause
		\item When does $G$ renew AD duties? \\
	\pause
  \vskip.1in
    $b(e,\tau^a,\tau^{\textit{ad}})$: probability $G$ prefers $\tau^{ad}$ to $\tau^a$ for a given effort level $e$
\end{itemize}

@@

\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 1}
  The total probability that $G$ renews AD duties is decreasing in the home trade agreement tariff $\tau^a$.
\end{beamerboxesrounded}

\vskip.25in
There's both a direct effect and an indirect effect through lobby's incentives, and both are negative:
\[
  \frac{\partial b}{\partial e} \frac{\partial e}{\partial \tau^a} + \frac{\partial b}{\partial \tau^a}
\]
\end{frame}

@@

Assuming trading partner does not retaliate
\begin{itemize}
	\item No difference in foreign tariff under AD duty and $\tau^a$. So no effect on $G$'s incentives (either direct or indirect)
\end{itemize}

\vskip.25in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 2}
  The total probability that $G$ renews AD duties is unaffected by foreign's trade agreement tariff $\tau^a$.
\end{beamerboxesrounded}
\end{frame}

@@

Assume $\pi(\cdot)$ shifts up uniformly for all $\tau$.
\begin{itemize}
	\item Convexity of profits $\Rightarrow$ $G$'s marginal benefit of providing protection goes up
	\item Convexity of profits $\Rightarrow$ return from lobbying increases
\end{itemize}

\vskip.25in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 3}
  The total probability that $G$ renews AD duties is increasing in the profitability of the import-competing sector.
\end{beamerboxesrounded}
\end{frame}

>>>>

\begin{frame}{Government}
  $G$ renews AD duties if its utility is higher under AD duties than trade agreement tariff
	\pause
  \begin{itemize}
		\item Preferences are ex-ante uncertain through $\ta$
		\pause
		\item When does $G$ renew AD duties? \\
	\pause
  \vskip.1in
    $b(e,\tau^a,\tau^{\textit{ad}})$: probability $G$ prefers $\tau^{ad}$ to $\tau^a$ for a given effort level $e$
\end{itemize}

@@

\pause
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 1}
  The total probability that $G$ renews AD duties is decreasing in the home trade agreement tariff $\tau^a$.
\end{beamerboxesrounded}

\vskip.25in
\pause
There's both a direct effect and an indirect effect through lobby's incentives, and both are negative:
\[
  \frac{\partial b}{\partial e} \frac{\partial e}{\partial \tau^a} + \frac{\partial b}{\partial \tau^a}
\]
\end{frame}

@@

Assuming trading partner does not retaliate
\pause
\begin{itemize}
	\item No difference in foreign tariff under AD duty and $\tau^a$. So no effect on $G$'s incentives (either direct or indirect)
\end{itemize}

\vskip.25in
\pause
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 2}
  The total probability that $G$ renews AD duties is unaffected by foreign's trade agreement tariff $\tau^a$.
\end{beamerboxesrounded}
\end{frame}

@@

\pause
Assume $\pi(\cdot)$ shifts up uniformly for all $\tau$.
\pause
\begin{itemize}[<+->]
	\item Convexity of profits $\Rightarrow$ $G$'s marginal benefit of providing protection goes up
	\item Convexity of profits $\Rightarrow$ return from lobbying increases
\end{itemize}

\vskip.25in
\pause
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 3}
  The total probability that $G$ renews AD duties is increasing in the profitability of the import-competing sector.
\end{beamerboxesrounded}
\end{frame}

[<+->]
\begin{frame}{Exogenous Shifts in $\ga(e,\ta)$}

\pause
Assume $\ga(\cdot,\cdot)$ shifts up uniformly for all $(e,\ta)$ pairs.
\pause
\begin{itemize}[<+->]
	\item $G$ gives more weight to firms' benefit
	\item Lobbying incentives are unchanged
\end{itemize}

\vskip.25in
\pause
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 3}
  The total probability that $G$ renews AD duties increases when the weighting function shifts up exogenously and uniformly.
\end{beamerboxesrounded}
\end{frame}

\begin{frame}{Protection from AD Duties}

\pause
When $\tau^{\textit{ad}}$ increases, two effects on $G$'s incentives:
\pause
\begin{itemize}[<+->]
	\item Social welfare decreases, pushes for decrease in renewal probability 
	\item (Over-weighted) import-competing profits increase, pushes for increase in renewal probability 
\end{itemize}

\vskip.2in
\pause
Indirect effect is of same sign as direct effect
\pause
\begin{itemize}[<+->]
	\item When $\tau^{\textit{ad}}$ (i.e. close to social optimum), second effect dominates $\Rightarrow$ increase in renewal probability
	\item Effect may be concave
\end{itemize}
